Properties of winning Iterated Prisoner's Dilemma strategies.

### 2020-03-30 paper/main.tex
Commit suggestion on line 138
Co-Authored-By: Nikoleta Glynatsi <GlynatsiNE@cardiff.ac.uk>

Other works have built upon the limitations of the TFT, and others have shown
that suggestions made by Axelrod did not necessarily lift to alternative environmental rules.
In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
that TFT suffered in environments with noise. This was
mainly due to the strategy's lack of generosity and contrition. Since TFT immediately
punishes a defection, in a noisy environment it can get stuck in a
repeated cycle of defections and cooperations. Some new strategies, more
robust in tournaments with noise, were soon introduced, including
Nice and Forgiving~\cite{Bendor1991}, Generous Tit For Tat~\cite{Nowak1992},
and Pavlov (aka Win Stay Lose Shift) ~\cite{Nowak1993}, as well as later
variants such as OmegaTFT \cite{kendall2007iterated}. Introduction of new strategies
is often accompanied by a claim that the new strategy is the best known despite
only being tested against a small number of opponents, or specific classes of
opponents not necessarily representative of all possible or all published strategies.
The lack of testing against formally defined strategies and tournament winners
is understandable given the effort required to implement
\footnote{Implementing prior strategies faithfully is often extremely difficult or impossible
due to insufficient descriptions and lack of published implementations or code.}
the hundreds of published IPD strategies, yet calls into question any claims of superiority
or robustness of newly introduced
strategies.

>>>>

Other works have built upon the limitations of the TFT, and others have shown
that suggestions made by Axelrod did not necessarily lift to alternative environmental rules.
In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
that TFT suffered in environments with noise. This was
mainly due to the strategy's lack of generosity and contrition. Since TFT immediately
punishes a defection, in a noisy environment it can get stuck in a
repeated cycle of defections and cooperations. Some new strategies, more
robust in tournaments with noise, were soon introduced, including
Nice and Forgiving~\cite{Bendor1991}, Generous Tit For Tat~\cite{Nowak1992},
and Pavlov (aka Win Stay Lose Shift)~\cite{Nowak1993}, as well as later
variants such as OmegaTFT \cite{kendall2007iterated}. Introduction of new strategies
is often accompanied by a claim that the new strategy is the best known despite
only being tested against a small number of opponents, or specific classes of
opponents not necessarily representative of all possible or all published strategies.
The lack of testing against formally defined strategies and tournament winners
is understandable given the effort required to implement
\footnote{Implementing prior strategies faithfully is often extremely difficult or impossible
due to insufficient descriptions and lack of published implementations or code.}
the hundreds of published IPD strategies, yet calls into question any claims of superiority
or robustness of newly introduced
strategies.
